---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statficlassifications

<!-- badges: start -->
<!-- badges: end -->

The `statficlassifications`-package allows the access to the classifications and correspondence tables open classifications API of Statistics Finland at https://data.stat.fi/api/classifications/v2. (For information on the API, see https://www.stat.fi/fi/luokitukset/info/.) `statficlassifications` gives functions that get correspondence tables / classification conversion keys and transform them into a format readily to be used by R. Also provides tools for reclassifying regions in data. 

## Installation

To install and start using the package:

```r
install.packages("devtools")
devtools::install_github("pttry/statficlassifications")
library(statficlassifications)
```

## Accessing API

```{r child = "vignettes/vignette_api_access.Rmd"}

```

## Tools for Regional Classifications

```{r child = "vignettes/vignette_region_classifications.Rmd"}

```

