---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# statficlassifications

<!-- badges: start -->
<!-- badges: end -->

The `statficlassifications` allows the access of Statistics Finland classifications API from within R. Gets correspondence tables or classification keys. Provides tools for reclassifying regions in data. 

## Installation

To install the packag and start using the package:

```{r}
install.packages("devtools")
devtools::install_github("pttry/statficlassifications")
library(statficlassifications)
library(dplyr)
```

## Searching and getting correspondence tables

### List all available classification keys

```{r}
search_keys()
```

### Search for available classifications

```r
search_keys("maakunta")
search_keys("maakunta", search_source = TRUE)
search_keys(searchword_source = "kunta", searchword_target = "maakunta", year = 2020)
```

### Print the localID of the search results and assign to variable

```r

localID <- search_keys(searchword_source = "kunta", searchword_target = "maakunta", year = 2020, as_localID = TRUE)
```

###  Create localID yourself

```r
localID <- create_localID_name("kunta", "maakunta", year = 2020)
```

### Get classification key

```r
key <- get_key(localID)
```

## Region classifications

The package aims to impose the use of prefixed region codes. Prefixes are useful in making sure codes do not map to multiple names. There are, for instance, kuntia and seutukuntia with identical numbers. Prefixes help distinguish between these.

The correpondence of region names and prefixes is 

```r
data(prefix_name_key); prefix_name_key
```

## Get the latest region key table

Load the complete regionkey

```r
key <- get_regionkey(only_codes = FALSE, only_names = FALSE)
```

## Manipulate region information in data

Generate random municipal data

```r
data <- get_regionkey() %>%
        dplyr::select(kunta_name) %>%
        mutate(values = rnorm(n()))
```

Use \code{dplyr::left_join} with this regionkey to add regions to your data

```r
left_join(data, get_regionkey(only_names = TRUE), by = "kunta_name")
```

Compute the region (maakunta) -level means.

```r
data %>% left_join(get_regionkey(only_names = TRUE), by = "kunta_name") %>% 
         group_by(maakunta_name) %>%
         summarize(maakunta_mean = mean(values)) 

```

Change municipality names to municipality codes

```r
data <- names_to_codes(data)
```

Change municpality codes to municipality names

```r
data <- codes_to_names(data)
```
