---
title: "package_structure"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{package_structure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(statficlassifications)
```

## Accessing and browsing API

### Accessing API

The core of the package are the functions for API access in the file `functions_for_api_access.R`. The function `access_API` accesses the open classification API of Statistics Finland. The functions `get_urls`, `get_keys` and `get_classifications` are wrappers of function `access_API` to get urls of endpoint, classification series and correspondence tables, respectively. 

Functions in this file should generally avoid using functions of this package. The function `find_classification_service` uses `search_keys` and `search_classifications`. This recursion works since the `search_keys` and `search_classifications`s set the argument `classification_service` and thus themselves do not rely on function `find_classification_service`. 

### Browsing API

File `functions_for_api_search.R` provides the tools for searching and browsing available classifications and classification keys in the API. Functions in this file rely on functions in file `functions_for_api_access.R`. There are two functions: `search_keys` and `search_classifications` corresponding to the two supported classification services correspondenceTables and classifications, respectively.
