---
title: "Recode with keys"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Recode with keys}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
  
  library(statficlassifications)

```

`statficlassifications` ships with a powerful tool to recode variables with keys and classifications. Recoding of categorical variables are often based on keys that map one classification of a categorical variable to an another classification of this same variable. `key_recode()` recodes an input given a such a key. The key can be in the form of a named vector or a data.frame. The inputs can be vectors, factors of data.frames. 

```{r}
var1 <- c("a", "b", "a", "c", "b", "b")

key <- data.frame(var1 = letters[1:4],
                  var2 = c("first letter",
                           "second letter",
                           "third letter",
                           "fourth letter"),
                  var3 = 1:4)
```

By default, the variable in key corresponding to the variable to be recoded is found by name:

```{r}
key_recode(var1, key, to = "var2")
```
The corresponding variable can however, be found using the values of variables as well:

```{r}
v <- var1
key_recode(v, key, to = "var2", by = "values")
```
data.frames can be recoded as well:

```{r}
df <- data.frame(var1 = var1,
                 y = 1:6)
key_recode(df, key, to = "var2")
```



Without 'to'-argument, recoding happens to all variable other than 'from'-variable in the key.

```{r}
key_recode(var1, key)
```

Keys can be named vectors as well:

```{r}
key <- c("a" = "first letter",
         "b" = "second letter",
         "c" = "third letter",
         "d" = "fourth letter")
```

```{r}
key_recode(v, key)
```
Note that with named vectors the function knows which way you are recoding:

```{r}
v <- key_recode(v, key)
v
v <- key_recode(v, key)
v
```

