---
title: "How to use"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include = FALSE}
library(statficlassifications)
library(dplyr)
```

# Searching for keys

To list all available keys, use `search_keys` without arguments:

```{r}
head(search_keys())
```

Plug in search terms to search for available keys or use more specific options:

```{r}
search_keys("maakunta")
search_keys("maakunta", search_source = TRUE)
search_keys(source = "kunta", target = "suuralue", year = 2020)
```

# Getting keys

Each key is uniquely identified by a local ID in the API. Having found the suitable key, you can use `search_keys` with an argument `as_localID = TRUE` to print the local ID of the key:

```{r}
localID <- search_keys(source = "kunta", target = "suuralue", year = 2020, as_localID = TRUE)
localID
```

You can also create a local ID yourself:

```{r}
localID <- create_localID_name("kunta", "maakunta", year = 2020)
localID
```

Finally, you can get the key by:

```{r}
key <- get_key(localID)
head(key)
```


