---
title: "How to use"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r include = FALSE}
library(statficlassifications)
library(dplyr)
```

There are two types of classification objects of interest: keys and classifications. Keys are used to convert between different classifications and classifications are can be used to convert names to codes and vice versa.

### Searching for keys

To list all available classification keys (correspondence tables), use `search_keys` without arguments:

```{r}
head(search_keys())
```

Plug in search terms to search for available keys or use more specific options:

```{r}
search_keys("maakunta")
search_keys("maakunta", search_source = TRUE)
search_keys(source = "kunta", target = "suuralue", year = 2020)
```

### Getting keys

The open classifications API uniquely identifies each classification key by a local ID. Having found the suitable key, you can use `search_keys` with an argument `as_localId = TRUE` to print the localId of the key:

```{r}
localId <- search_keys(source = "kunta", target = "suuralue", year = 2020, as_localId = TRUE)
localId
```

Then you can get the key by:

```{r}
key <- get_key(localId)
head(key)
```

### Searching for classifications

To list all available classifications, use `search_classifications` without arguments:

```{r}
head(search_classifications())
```

Plug in search terms to search for available classifications or use more specific options:

```{r}
search_classifications("ammatti")
search_classifications("ammatti", year = 2021)
```

### Getting classifications

To print the localId of the desired classification, use `as_localId = TRUE`.

```{r}
localId <- search_classifications("ammatti", year = 2021, as_localId = TRUE)
```

Use localId to get the classification

```{r}
head(get_classification(localId))
```

